Untitled

### 2022-12-13 draft1_Rcode.Rmd
Creating code for Q5 (check with code where know there are 3 groups)

```{r}
## Question 5
#a
bootFStat <- function(group,y,w,bootCount){
  #iterating for each replicate
  for (b in 1:bootCount){
    #creating bth bootstrap dataset
    sample(y)
  }

}

#b
eco.df <- read.table("q5EcoStudy.txt",header = T)
```

>>>>

```{r}
#Q5 but with unknown number of groups

#a
bootFStat <- function(group,y,w,bootCount){
  #object to store B bootstrap estimates of f statistic
  Fstat.boot.est <- NULL
  #grouping values into dataset 
  data <- data.frame("group"=group,"Obs"=y,"weight"=w)
  #Adding id column so can sample by id to retain all info of row (obs and weight)
  data$id <- seq(1,dim(data)[1])

  for (b in 1:bootCount){
    #object to store value of y tidle * N 
    y.tilde.N <- 0

    #loop to do bootstrap method for each group
      for (group_val in unique(data$group)){
        #selecting subset id's of dataset that is current group
        group_dataset <- data$id[data$group==group_val]
        #sampling from group dataset with replacement
        group_sample.id <- sample(group_dataset, size = length(group_dataset), replace = TRUE)

          #Using sampled id to select obs and weight for each id sampled to create bootstrap dataset for each group
          #Selecting obs and weights using id's sampled
          sample.group.obs <- NULL
          sample.group.weight <- NULL

          for (i in 1:length(group_sample.id)){
            sample.group.obs[i] <- data$Obs[data$id == group_sample.id[i]]
            sample.group.weight[i] <- data$weight[data$id == group_sample.id[i]]
          }
          #Setting sampled observations and weights to be those of group they belong to before repeating loop with next group
          assign(paste0("sample.",group_val,".obs"),sample.group.obs)
          assign(paste0("sample.",group_val,".weight"),sample.group.weight)

          #Calculating y tilde_{i} for current group
          y.tilde.group <- sum(sample.group.obs*sample.group.weight)/length(sample.group.obs)
          assign(paste0("y.tilde.",group_val),y.tilde.group)

          #updating y tilde using current group
          y.tilde.N <- y.tilde.N + sum(sample.group.obs*sample.group.weight)

          #Calculating part of denominator of f-statistic corresponding to current group
          f.denom.group.part <- sum((sample.group.obs*sample.group.weight-y.tilde.group)^2)
          assign(paste0("f.denom.",group_val),f.denom.group.part)
      }

    #calculating y tilde
    y.tilde <- y.tilde.N/length(y)
    # y.tilde <- y.tilde.N/300

    #calculating summation parts of numerator and denominator of f statistic
    fstat.num <- 0
    fstat.denom <- 0
    for (group_val in unique(data$group)){
      fstat.num <- fstat.num+length(get(paste0("sample.",group_val,".obs")))*(get(paste0("y.tilde.",group_val))-y.tilde)^2
      fstat.denom <- fstat.denom + get(paste0("f.denom.",group_val))
    }
    #calculating F stat
    fstat <- (fstat.num/(length(unique(group))-1))/(fstat.denom/(length(y)-length(unique(group))))
    Fstat.boot.est[b] <- fstat
  }

  #Calculating standard error of bootstrap f statistic
  bootstr.mu <- sum(Fstat.boot.est)/length(Fstat.boot.est)
  bootstr.se <- sqrt(sum((Fstat.boot.est-bootstr.mu )^2)/(length(Fstat.boot.est-1)))

  return(bootstr.se)
}

#b
set.seed(2022)
bootFStat(eco.df$habitat,eco.df$density,eco.df$weight,1000)

```

```{r}
## Question 5 extra stuff

#a
unique(eco.df$habitat)[3]

bootFStat <- function(group,y,w,bootCount){
  #grouping into dataset 
  data <- data.frame("group"=group,"Obs"=y,"weight"=w)
  #Adding id column so can sample by id to retain all info of row (obs and weight)
  data$id <- seq(1,dim(data)[1])

  #Splitting data into groups depending on group
  group.A <- data$id[data$group=="A"]
  group.B <- data$id[data$group=="B"]
  group.C <- data$id[data$group=="C"]
  #Sampling with replacement
  sample.A.id <- sample(group.A, size = length(group.A), replace = TRUE)
  sample.B.id <- sample(group.B, size = length(group.B), replace = TRUE)
  sample.C.id <- sample(group.C, size = length(group.C), replace = TRUE)

  #Using sampled id to select obs and weight for each id sampled to create bootstrap dataset for each group
  #Selecting obs and weights using id's sampled

  #For A
  sample.A.obs <- NULL
  sample.A.weight <- NULL
  for (i in 1:length(sample.A.id)){
    sample.A.obs[i] <- data$Obs[data$id == sample.A.id[i]]
    sample.A.weight[i] <- data$weight[data$id == sample.A.id[i]]
  }
  #calculating y.tilde_{i} for A
  y.tilde.A <- sum(sample.A.obs*sample.A.obs)/length(sample.A.obs)

  #For B
  sample.B.obs <- NULL
  sample.B.weight <- NULL
  for (i in 1:length(sample.B.id)){
    sample.B.obs[i] <- data$Obs[data$id == sample.B.id[i]]
    sample.B.weight[i] <- data$weight[data$id == sample.B.id[i]]
  }
  #calculating y.tilde_{i} for B
  y.tilde.B <- sum(sample.B.obs*sample.B.obs)/length(sample.B.obs)

  #For C
  sample.C.obs <- NULL
  sample.C.weight <- NULL
  for (i in 1:length(sample.C.id)){
    sample.C.obs[i] <- data$Obs[data$id == sample.C.id[i]]
    sample.C.weight[i] <- data$weight[data$id == sample.C.id[i]]
  }
  #calculating y.tilde_{i} for C
  y.tilde.C <- sum(sample.C.obs*sample.C.obs)/length(sample.C.obs)

  #Calculating y.tilde
  y.tilde <- (y.tilde.A*length(sample.A.obs)+y.tilde.B*length(sample.B.obs)+y.tilde.C*length(sample.C.obs))/length(y)

  #Calculating F.tilde
  F.num <- 1
  F.denom <-2
}

library(dplyr)
eco.df <- read.table("q5EcoStudy.txt",header = T)
data <- eco.df%>%
  rename("group"="habitat","Obs"="density")
data$id <- seq(1,dim(data)[1])

  #Splitting data into groups depending on group
  group.A <- data$id[data$group=="A"]
  group.B <- data$id[data$group=="B"]
  group.C <- data$id[data$group=="C"]
  #Sampling with replacement
  sample.A.id <- sample(group.A, size = length(group.A), replace = TRUE)
  sample.B.id <- sample(group.B, size = length(group.B), replace = TRUE)
  sample.C.id <- sample(group.C, size = length(group.C), replace = TRUE)

  #Using sampled id to select obs and weight for each id sampled to create bootstrap dataset for each group
  #Selecting obs and weights using id's sampled

  #For A
  sample.A.obs <- NULL
  sample.A.weight <- NULL
  for (i in 1:length(sample.A.id)){
    sample.A.obs[i] <- data$Obs[data$id == sample.A.id[i]]
    sample.A.weight[i] <- data$weight[data$id == sample.A.id[i]]
  }
  #calculating y.tilde_{i} for A
  y.tilde.A <- sum(sample.A.obs*sample.A.obs)/length(sample.A.obs)

#b
eco.df <- read.table("q5EcoStudy.txt",header = T)

test
```
